---
title: "Reproducible Research: Assignment One"
author: "Sean Sebry"
date: "2020-01-16"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, results = 'hide', eval = TRUE)

```

## **The Quantified Self Data**

### Vignette initialization:

Assignment conditions 1, 9

```{r load packages, results = 'hide', message = FALSE}

#If not installed:
#install.packages("tidyverse")
#install.packages("data.table")

library(tidyverse)
library(data.table)
library(lubridate)

```

### Exploratory data analysis:

Assignment conditions 1, 2, 9

```{r eda, results = 'markup'}

data_raw <- fread("activity.csv")
head(data_raw)
str(data_raw)

#Sample histogram of total steps taken each day (with out removing missing data)

```

- steps: Number of steps taking in a 5-minute interval (missing values are coded as \color{red}{\verb|NA|}NA)
- date: The date on which the measurement was taken in YYYY-MM-DD format
- interval: Identifier for the 5-minute interval in which measurement was taken

*source: assignment document*

### Tidying

Assignment conditions 6, 9

```{r data tidying, results='markup'}

# Note, for the assignment, my strategy and method to analyze this data, is to only use complete observations, as seen in this code: (this code is meant to satisfy assignment condition 6.)
data_tidy <- data_raw %>% 
  mutate(date = as_date(date)) %>% 
  filter(complete.cases(.)) %>% 
  glimpse()

```

### Analysis

1. Steps taken each day

Assignment conditions 7, 9

```{r data analytics 1, results='markup'}

total_steps_by_day <- data_tidy %>% 
  group_by(date) %>% 
  summarize(steps_per_day = sum(steps)) %>% 
  print()

total_steps_by_day_plot <- ggplot(total_steps_by_day, aes(x = steps_per_day))
total_steps_by_day_plot +
  geom_histogram(bins = nrow(total_steps_by_day)) + 
  labs(title = "Histogram of Steps per Day")

```

2. Statistics of steps per day

Assignment conditions 3, 4, 9

```{r data analytics 2, results='markup'}

stats_for_steps_by_day <- data_tidy %>% 
  filter(steps > 0) %>% 
  group_by(date) %>% 
  summarize(avg_steps_per_day = mean(steps), median_steps_per_day = as.integer(median(steps))) %>% 
  print()

long_form_stats_for_steps_by_day <- reshape2::melt(stats_for_steps_by_day, id = "date")

ggplot(data=long_form_stats_for_steps_by_day,
       aes(x=date, y=value, colour=variable)) +
       geom_line() +
       labs(title = "Median and mean (non-zero) steps per day")

```

3. The 5 minute interval that on average 

Assignment conditions 5, 8, 9

```{r data analytics 3, results='markup'}



```





